MSDS 6372 Project 1 Objective 1

### 2020-02-11 Codebook/MSDS6372.Project.O1.Rmd
Update MSDS6372.Project.O1.Rmd

rfitl <- lm(log(price) ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = nyc4)
summary(rfitl)
plot(rfitl)

```

>>>>

rfitl <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc4)
summary(rfitl)
plot(rfitl)
```
